Distributions

### 2021-12-28 Ch2_distributions/Ch2_Figures.Rmd
Figure 4 caption.

@@

What about the parameters of the best fit distributions? Meaning, that for each boostrap, keep only the best model. Plot those.

>>>>

Figure 4 - Delta BIC values for each bootstrap in the three pooling scenarios. Each bootstrap is represented in the y axis, with BIC units from the best model shown in the x axis. For the first panel, the CP scenario shows significant overlap among models for each bootstrap. Given that multi distribution models for the PP and NP scenarios have 100% support, this means they have the lowest BIC score, or a $\Delta$ BIC equal to zero, and thus show as a straight line at x=0 in the plots above.

@@

# Appendix figures

To tell the same story, we see variation in the parameters estimated for each bootstrap under various models.
